Virginia Tech, a University in Virginia, USA, has developed a fixed wing drone called the EcoSoar; a flying wing.
It is an aircraft designed for fabrication, operation and maintenance in low-
resource environments.
The total cost of one EcoSoar is only around 350 USD when costs for all tools and materials have been accounted for and spread over ten aircraft.

EcoSoar has been successfully flown in Malawi at
the test corridor established by UNICEF in Kasungu,
where a simulated payload of dried blood spot sam-
ples (used for HIV testing) was delivered 19 km from
a remote health clinic to the Kasungu airport. The
aircraft is constructed of poster-board and 3D printed
parts, making it easy to source in Malawi and low-
cost to repair if damaged.

Many flight operations occurring in Africa are converging on hybrid aircraft designs where the aircraft functions as a quadcopter in takeoff and landing but is capable of higher speed flight in a fixed wing configuration.

EcoSoar can currently be launched with a big bungee-cord or with a custom built launcher. It thus needs a field to both take off and land in since it can only land on its belly similar to that of any normal aircraft.
Modifying the EcoSoar to have two engines, one on the front of each wing, instead of the current design of having one at the back, might allow it to hover, take off and land vertically eliminating the need for a launching system as well as the requirement of a big field for take-off and landing.

Adding VTOL capacity to this drone would greatly increase its range of possible missions and thus help humanitarian efforts centered around EcoSoar in Malawi.

To achieve VTOL not only is hardware modifications necessary but also a new control scheme is necessary.